A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-10-16 review2/response.letter.tex

\documentclass[journal,onecolumn,12pt]{IEEEtran}

\usepackage{amsmath,amssymb,bm}
\usepackage{amsthm, amsfonts}	
\usepackage{bm,bbm}
\usepackage[normalem]{ulem}
\usepackage{color}
\usepackage{fancybox}
\usepackage{url,booktabs}
\usepackage[round]{natbib}

\usepackage{xr}

\title{2nd Reply to Reviewer's Comments on\\
``A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation''}
\author{}

\begin{document}

\maketitle
\pagenumbering{roman}
\setcounter{page}{1}

We appreciate a lot all the comments provided by the Reviewers and the AE.

In the following, we discuss our responses to pointed out issues.

\vskip+1ex
\noindent \dotfill

\section*{\fbox{Associate Editor Transcript:}}

Associate Editor Comments to Author:

Associate Editor
Comments to the Author:
Most of the comments expressed by the two Reviewers have been successfully addressed. As a result, the clarity of the paper improved significantly. There remain some very minor issues, which I list below for the Authors' convenience.

\begin{itemize}
\item Better define $l_R$ and $l_L$, which probably could be named "changes in length".
\item Please avoid the use of the word "longitude".
\item The content of Section VII-A (Validation experiments) should be part of the "Results" sections, i.e. Sec. IV,V.
\item Amend the remaining typos and link up all the references.
\end{itemize}

\section*{\fbox{Reviewer \#1 Transcript:}}

The work presented in this work is extremely interessant and of paramount importance for help in the medical field, since it frees not needed medical personel to help in other tasks thus improving patient care.

The manuscript is very well written with some typos I will refer in short. Besides those minor issues I did not find any issues the require reviewing, the addition of sections III and VII as well as the rewriting of section II.D have greatly improved the quality of the manuscript, allowing for the readers to better understand the proposed system and the technology behind it making possible for the system to be used to its fullest extent as well as for improvements to the system to be made even by groups outside the authors of the manuscript.

Thus, I would like to congratulate the authors on the work done and on the manuscript.

Finally, there are some typos I feel need to be addressed for this manuscript to be of examplar quality, these are:
on section I, line 11, it reads "waking activities" when it should be "walking activites"
on section I, line 18, it reads "their own condition prevent them" and it should be "their own condition prevents them"
on section VII, beginning of the second paragraph, it reads "Each control strategy has its advantages, but according various" and it should be "Each control strategy has its advantages, but according to various"

\section*{\fbox{Reviewer \#2 Transcript:}}

The revisions the authors have made have improved the manuscript - thank you for implementing those. At this stage, I have a few remaining concerns.

- The word definitions of $l_R$ and $l_L$ are still unclear. They are introduced as differences in length, but then also referred to as "thread longitudes". I find the term "longitude" here to be confusing given that these length differences can have a non-horizontal component if the target is at some angle from the reel (i.e., they are not purely longitudinal measurements, but rather can be seen as two vectors pointing to the same point in 2D space with both x and y components). My recommendation is that these definitions be further clarified.

- In Algorithm 1, as far as I can tell, no definition is provided for $D_t$, $D_m$, nor $base_{vr}$. This should be remedied.

- I believe Section III B. can be improved by being even more explicit about the specific improvements in the current design vs. the existing design. Section III, in general, reads as-if these designs are just equivalent (which begs the question: "why was this work done then?")

- Finally, the validation experiments with the oxygen tank (Section VIIA) should not be in the concluding remarks, but rather more tightly integrated into the experimental results section (Sections IV/V) with accompanying discussion.

\section*{\fbox{Associate Editor Responses:}}

Associate Editor Comments to Author:

Associate Editor
Comments to the Author:
Most of the comments expressed by the two Reviewers have been successfully addressed. As a result, the clarity of the paper improved significantly. There remain some very minor issues, which I list below for the Authors' convenience.

\begin{itemize}
\item Better define $l_R$ and $l_L$, which probably could be named "changes in length".
\item Please avoid the use of the word "longitude".
\item The content of Section VII-A (Validation experiments) should be part of the "Results" sections, i.e. Sec. IV,V.
\item Amend the remaining typos and link up all the references.
\end{itemize}

\begin{quotation}
{\color{blue}
We thank gratefully to the Associate Editor for their comments and suggestions.

\vspace{10pt}

Regarding the first two issues we have fixed them following Reviewer's  suggestions.  We have clarified missing terms definitions and the word "longitude" is not used anymore in the manuscript.  In relation with the third issue, we have modified the manuscript's structure as per Reviewer's recommendation to provide more readability.   Finally, regarding the fourth issue, we have fixed all the pointed out typos and verified all the references.

\vspace{10pt}

We appreciate a lot the time taken by the AE and all the Reviewers.
}
\end{quotation}

\section*{\fbox{Reviewer \#1 Responses:}}

%\subsection*{\ovalbox{Reviewer 1 General Comments}}

The work presented in this work is extremely interessant and of paramount importance for help in the medical field, since it frees not needed medical personel to help in other tasks thus improving patient care.

The manuscript is very well written with some typos I will refer in short. Besides those minor issues I did not find any issues the require reviewing, the addition of sections III and VII as well as the rewriting of section II.D have greatly improved the quality of the manuscript, allowing for the readers to better understand the proposed system and the technology behind it making possible for the system to be used to its fullest extent as well as for improvements to the system to be made even by groups outside the authors of the manuscript.

Thus, I would like to congratulate the authors on the work done and on the manuscript.

Finally, there are some typos I feel need to be addressed for this manuscript to be of examplar quality, these are:
on section I, line 11, it reads "waking activities" when it should be "walking activites"

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We fixed this typo, thanks a lot for pointing out this.
}
\end{quotation}
\vspace{10pt}

on section I, line 18, it reads "their own condition prevent them" and it should be "their own condition prevents them"

\vspace{10pt} 
\begin{quotation}
{\color{blue}
Fixed.
}
\end{quotation}
\vspace{10pt}

on section VII, beginning of the second paragraph, it reads "Each control strategy has its advantages, but according various" and it should be "Each control strategy has its advantages, but according to various"

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We also fixed this grammar error.  We appreciate a lot the careful reading of our manuscript.
}
\end{quotation}
\vspace{10pt}

\section*{\fbox{Reviewer \#2 Responses:}}
%\subsection*{\ovalbox{Reviewer 2 General Comments}}

The revisions the authors have made have improved the manuscript - thank you for implementing those. At this stage, I have a few remaining concerns.

- The word definitions of $l_R$ and $l_L$ are still unclear. They are introduced as differences in length, but then also referred to as "thread longitudes". I find the term "longitude" here to be confusing given that these length differences can have a non-horizontal component if the target is at some angle from the reel (i.e., they are not purely longitudinal measurements, but rather can be seen as two vectors pointing to the same point in 2D space with both x and y components). My recommendation is that these definitions be further clarified.

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We have modified on Section II.D, at the end of page 3, and clarified the terms according to the Reviewer suggestion.  They are indeed changes in the length of the thread released from each reel.  We have eliminated the use of the confusing term "longitude".  
}
\end{quotation}
\vspace{10pt}

- In Algorithm 1, as far as I can tell, no definition is provided for $D_t$, $D_m$, nor $base_{vr}$. This should be remedied.

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We have included in Section II, page 4, the definition of $base_{vr}$ which was missing, and also clarified that $D_t$, $D_m$ are temporary variables used to perform the calculations on Algorithm 1.
}
\end{quotation}
\vspace{10pt}

- I believe Section III B. can be improved by being even more explicit about the specific improvements in the current design vs. the existing design. Section III, in general, reads as-if these designs are just equivalent (which begs the question: "why was this work done then?")

\vspace{10pt} 
\begin{quotation}
{\color{blue}
Underway
}
\end{quotation}
\vspace{10pt}

- Finally, the validation experiments with the oxygen tank (Section VIIA) should not be in the concluding remarks, but rather more tightly integrated into the experimental results section (Sections IV/V) with accompanying discussion.

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We appreciate the Reviewer suggestion.  We have modified the manuscript structure following the Reviewer recommendation.  There is now a new Section V.A which included this experimental simulation.
}
\end{quotation}
\vspace{10pt}

\vskip+1ex
\noindent \dotfill
\vskip+1ex
\bibliographystyle{mdpi}
\bibliography{article}

\end{document}

### 2020-10-16 alpibot.1.tex
Versión casi lista, integrada con los cambios de Luciano.  Solo falta la aclaración de Juan.

\author{Bianchi Luciano, Buniak Esteban Alejandro, Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        and Santos~Juan~Miguel% <-this % stops a space
\thanks{E. A. Buniak, R. Ramele  and J.M.Santos are with the CIC Laboratory at the Department
of  Computer Engineering, Instituto Tecnológico de Buenos Aires (ITBA), Ciudad de Buenos Aires,  Argentina e-mail: rramele@itba.edu.ar}% <-this % stops a space
\thanks{Manuscript received May 16, 2020; revised July 6, 2020.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) undergo a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  Pulmonary Rehabilitation consists of different physical exercises and walking activities conducted at medical facilities under supervision of a physical therapist.  In order to perform these procedures, patients require oxygen assistance, but the oxygen tank cannot be carried by the patient due to the musculoskeletal atrophy that characterize this pathology and external assistance is required.   The assistance to transport the bulky oxygen tank can be provided by a robotic device that follows the patient while performing the physical activities. This work provides an initial study on the controlling mechanism of a differential tethered robot that implements a leader-follower configuration to carry the oxygen tank for these procedures.  Two alternative control strategies are proposed.  Results on a simulated and on a real prototype confirms the feasibility of the proposed solution.
\end{abstract}

%Results on a simulated and on a real prototype, and external validation from professional healthcare givers, confirm the feasibility of the proposed solution.
%While performing Pulmonary Rehabilitation patients perform different exercises and walking activities and may require oxygen assistance.

%Pulmonary Rehabilitation procedures consist of controlled walking activities and physical exercises that patients perform under the supervision of a physical therapist.

@@

\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents a musculoskeletal atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  Pulmonary Rehabilitation procedures consist of controlled walking activities and physical exercises that patients perform under the supervision of a physical therapist.  However, COPD patients present a severe low oxygen saturation illness and they require oxygen supply, particularly when performing physical activities~\cite{Celli2014}.  Hence, they are required to carry an oxygen tank for the oxygenotherapy assistance, but their own condition hinders their ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  The scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologists and physical therapists.

@@

An alternative solution is to use an assitive ground service robot~\cite{Neto2015} to carry the oxygen tank while following the patient in a leader-follower configuration.  There are two reasons that support the initial viability of this idea.  First,  the rehabilitation gym is a constrained environment where this problem can be tackled by an Unmanned Ground Vehicle (UGV).  On the other hand, the range of movements performed by the patient during the Rehabilitation Procedure is highly predictable by the treatment.  At the same time,  the global robotic research community looks forward for the development of robotic affordable solutions to social and health-related worldwide problems~\cite{Khamis2019}.

@@

Hence, this work provides an initial study on the controlling mechanism of a differential tethered robot that implements the leader-follower configuration on a Pulmonary Rehabilitation procedure.  To do so, this document unrolls as follows.  Section~\ref{materials} and~\ref{Comparison} poses the problem and the solution design. Section~\ref{experimental} documents the experimental protocol to perform the solution assessment on a simulation and on a real world scenario.  Results and discussions are described in Sections ~\ref{results} and~\ref{discussion}. The clinical assessment performed jointly with medical personnel is tackled in Section~\ref{clinical}.  Finally, conclusions are exposed in the remaining Section~\ref{conclusion}.

@@

To be effective, any technological solution for the medical community requires active involvement of key stakeholders: physicians, care-givers, patients and their families~\cite{Gaggioli2006,Fasola2012,Cherubini2008,Wolpaw2012BraincomputerIP,Salvini2015}.  Hence, design methodologies that allow rapid prototyping can bring quick feedback from real users about drawbacks or opportunities for improvements.

@@

    % Text Node
    \draw  [draw opacity=0][fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ]  (478.5,1350) -- (535.5,1350) -- (535.5,1374) -- (478.5,1374) -- cycle  ;
    \draw (517,1362) node    {$subject$};
    % Text Node
    \draw (302,1344) node    {$left\ reel\  \ $};
    % Text Node
    \draw (299,1425) node    {$right\ reel\  \ $};
    % Text Node
    \draw (125,1414) node    {$castor\ wheel$};
    % Text Node
    \draw (422,1348) node  [rotate=-12.55]  {$left\ thread$};
    % Text Node
    \draw (423,1422) node  [rotate=-344.79]  {$right\ thread$};
    % Text Node
    \draw (348,1275) node    {$left\ wheel$};
    % Text Node
    \draw (348,1496) node    {$right\ wheel$};
    \end{tikzpicture}
    \caption{Components of the robotic vehicle and the tether mechanism}
    \label{fig:components}
\end{figure}{}

@@

% El detalle de los encoders se puede eliminar, es info común.
Encoders in each reel measure the difference in length of each thread compared to its initial position. These differences in length are the input for the control algorithm.  Using the encoder, the difference in length for each thread can be measured with Equations~\ref{eq:encoder_len}.

\begin{equation}
\label{eq:encoder_len}
\begin{array}{ll}  
l_L = pulses_{l} \; \frac{2\pi r}{ppr}  \\
\\
l_R = pulses_{r} \; \frac{2\pi r}{ppr}
\end{array}
\end{equation}{}

\noindent where $pulses_{l}$ and $pulses_{r}$ are the pulses obtained for the left and right encoder.  Pulses refer to natural discrete numbers that represents the circular movement of the encoder shaft.  The variable $r$ is the radius of the reel and $ppr$ is the pulses per revolution (resolution) of the encoder. These equations provide the estimated values for the left $l_L$ and right $l_R$  thread longitude.   The initial position of the threads is configurable.

@@

The SBC connects to a WiFi network and can receive remote commands to control the robot. It also broadcasts telemetry data to any listening devices on the network. The control algorithms run in this board, which continuously communicates with the Arduino board to receive sensor data and to issue commands to move the motors or retract the reels.   The algorithms are programmed in Python 3.7, which allows the exact same code to run both the simulated and real world prototype.

@@

The two reels are designed from PVC extrusions and are shown on Figure~\ref{fig:alpibot2}.  They are attached to regular FA-12350 DC motors scavenged from old compact discs.  Each reel is axially locked to inexpensive Ky-040 rotary encoder~\cite{SugaharaJunOnoKoji1998} which provides around 20 pulses per revolution.
%Hardware specifications are described on table \ref{tab:specifications}.

@@

As previously mentioned, an active spring mechanism is also put in place to keep the threads tense.  However, in order to extend the useful life of the reel motors, and to save battery, an algorithm to  activate and deactivate the motors was developed.

@@

Two simple algorithmic control strategies are proposed and evaluated.  The first one is called \textit{Follow the thread} and the second strategy is \textit{Rotate and go}.  %The Adafruit Shield controller provides a very stable output signal, provided battery are kept above reference.  Hence, wheels motor control is open-loop.

@@

This control strategy is similar to the one presented in \cite{Ortlieb2016}.  It is based on the idea that both the relative angle between the subject and the vehicle orientation and, the relative distance between the robot and the subject, can be computed from the length of the left and right threads.  They are described by Equations~\ref{eq:lemniscata}, \ref{eq:lemniscata2} and~\ref{eq:lemniscata3}.

\begin{equation}
V_t = c_v (\frac{l_L + l_R}{2} - l_D)
\label{eq:lemniscata}
\end{equation}

\begin{equation}
\omega_{L} = V_t + c_{\alpha} (l_L - l_R)
\label{eq:lemniscata2}
\end{equation}

\begin{equation}
\omega_{R} = V_t - c_{\alpha} (l_L - l_R)
\label{eq:lemniscata3}
\end{equation}

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration whose units are expressed in $[\frac{1}{s}]$, and $l_D$ is a constant offset in $[m]$ that is used to customize the desired length of the thread where the robot does not move.   As shown on Figure~\ref{fig:follow_params},  $l_L$ and $l_R$ are changes in thread longitudes (the length of thread that was released from each reel) in $[m]$  obtained from encoder information from Equation~\ref{eq:encoder_len}, $V_t$ is the estimated forward velocity for the target and finally $\omega_{L}$ are $\omega_{R}$ are the velocity values that are directly used to drive each wheel motor.

@@

\begin{equation}
\textit{if  }{\frac{l_L + l_R}{2} < l_D}\textit{ then } \omega_{L} = \omega_{R} = 0.
\end{equation}

@@

    % Text Node
    \draw (524,1960) node  [font=\large,color={rgb, 255:red, 74; green, 144; blue, 226 }  ,opacity=1 ]  {$ \begin{array}{l}
    l_{R}\\
    \end{array}$};
    % Text Node
    \draw (510,1910) node  [font=\large,color={rgb, 255:red, 74; green, 144; blue, 226 }  ,opacity=1 ,rotate=-358.27]  {$ \begin{array}{l}
    l_{L}\\
    \end{array}$};
    % Text Node
    \draw (496,2042) node  [color={rgb, 255:red, 128; green, 128; blue, 128 }  ,opacity=1 ]  {$subject\ start$};
    % Text Node
    \draw  [draw opacity=0][fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ]  (554.5,1904) -- (611.5,1904) -- (611.5,1928) -- (554.5,1928) -- cycle  ;
    \draw (583,1916) node    {$subject$};
    % Text Node
    \draw (390.58,1925.93) node [anchor=west] [inner sep=0.75pt]  [font=\normalsize,color={rgb, 255:red, 0; green, 0; blue, 0 }  ,opacity=1 ]  {$\omega_{L}$};
    % Text Node
    \draw (407.58,2100.93) node [anchor=west] [inner sep=0.75pt]  [font=\normalsize,color={rgb, 255:red, 0; green, 0; blue, 0 }  ,opacity=1 ]  {$\omega_{R}$};

@@

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_{off}$ that regulates the sensibility of the rotation movement.  The constant parameter $Dm_{off}$ is similar to $l_D$, and is used to customize the length of the thread where the robot does not move at all. Lastly, $base_{vr}$, is another constant used to determine the minimum rotational velocity of the vehicle.

\begin{algorithm}[]
\caption{Rotate and go algorithm}
\begin{algorithmic}
\STATE $Dt \gets l_L - l_R$
\STATE $Dm \gets \frac{l_R+l_L}{2}$
\STATE $V_r \gets c_r * (abs(Dt) - Dt_{off}) + base_{vr}$ 
\STATE $V_f \gets c_v * (Dm - Dm_{off})$

\IF{$abs(Dt) > Dt_{off}$}
\IF{$l_L > l_R$}
\STATE $\omega_{L} \gets V_r$
\STATE $\omega_{R} \gets -V_r$
\ELSE
\STATE $\omega_{L} \gets -V_r$
\STATE $\omega_{R} \gets V_r$
\ENDIF

\ELSE
\IF{$D_m > Dm_{off}$}
\STATE $\omega_{R} \gets V_f$
\STATE $\omega_{L} \gets V_f$
\ELSE
\STATE $\omega_{R} \gets 0$
\STATE $\omega_{L} \gets 0$
\ENDIF
\ENDIF
\STATE Return $\omega_{R}$ and $\omega_{L}$.
\end{algorithmic}
\label{alg:rotateandgoalg}
\end{algorithm}

\section{Comparison with alternative methods} \label{Comparison}

\subsection{Equivalence between the single and double tethered system}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=8cm]{images/dibujito.jpg}
%\caption{Scheme of the equivalence between a single and dual thread systems.}
%\label{fig:dibujito}
%\end{figure}

In~\cite{Endo2015} authors propose a similar design based on only one thread.  They propose two control strategies based on two input parameters that are obtained from a linear and circular potentiometer that determines the length of the thread $l_m$ and the orientation angle $\theta$.  We show here that they are equivalent to the approach presented based on $l_L$ and  $l_R$.

Based on a frame reference with the robot on the center of coordinates as shown on Figure~\ref{fig:dibujitos}, from the input values $l_m$ and $\theta$ we can derive the position of the leader as

\begin{align*}
   y &= l_m  \cos(\theta)\\
   x &= l_m  \sin(\theta) \\
\end{align*}

%From the figure, it can be obtained that
%
%\begin{align*}
%x'            	&= \frac{b}{2}  - x \\
%x'' 			&= \frac{b}{2}  + x \\
%\end{align*}
%

\noindent where $x$ is the follower distance on the horizontal direction, and $y$ the follower distance on the vertical direction.

In this frame of reference, the lengths of the threads, $l_R$ and $l_L$ can be determined as

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,235); %set diagram left start at 0, and has height of 235

%Shape: Axis 2D [id:dp7543865369052545] 
\draw  (312,162.89) -- (521,162.89)(332.9,2.69) -- (332.9,180.69) (514,157.89) -- (521,162.89) -- (514,167.89) (327.9,9.69) -- (332.9,2.69) -- (337.9,9.69)  ;
%Rounded Same Side Corner Rect [id:dp31787525316857024] 
\draw   (297.9,150.89) .. controls (297.9,146.47) and (301.48,142.89) .. (305.9,142.89) -- (359.9,142.89) .. controls (364.32,142.89) and (367.9,146.47) .. (367.9,150.89) -- (367.9,182.89) .. controls (367.9,182.89) and (367.9,182.89) .. (367.9,182.89) -- (297.9,182.89) .. controls (297.9,182.89) and (297.9,182.89) .. (297.9,182.89) -- cycle ;
%Shape: Square [id:dp8026938389823051] 
\draw   (434,151.69) -- (457,151.69) -- (457,174.69) -- (434,174.69) -- cycle ;
%Shape: Square [id:dp06857182701706144] 
\draw   (207.66,149.66) -- (231.34,149.66) -- (231.34,173.34) -- (207.66,173.34) -- cycle ;
%Flowchart: Summing Junction [id:dp2757072161924359] 
\draw   (317.9,162.89) .. controls (317.9,155.16) and (324.62,148.89) .. (332.9,148.89) .. controls (341.18,148.89) and (347.9,155.16) .. (347.9,162.89) .. controls (347.9,170.62) and (341.18,176.89) .. (332.9,176.89) .. controls (324.62,176.89) and (317.9,170.62) .. (317.9,162.89) -- cycle ; \draw   (322.29,152.99) -- (343.51,172.79) ; \draw   (343.51,152.99) -- (322.29,172.79) ;
%Straight Lines [id:da9717478160302964] 
\draw [line width=2.25]    (405,12.69) -- (332.9,162.89) ;
%Straight Lines [id:da30114532827552765] 
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=2.25]    (405,12.69) -- (219.5,161.5) ;
%Straight Lines [id:da0582330345196298] 

>>>>

\author{Bianchi Luciano, Buniak Esteban Alejandro, Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        and Santos~Juan~Miguel% <-this % stops a space
\thanks{E. A. Buniak, R. Ramele  and J.M.Santos are with the CIC Laboratory at the Department
of  Computer Engineering, Instituto Tecnológico de Buenos Aires (ITBA), Ciudad de Buenos Aires,  Argentina e-mail: rramele@itba.edu.ar}% <-this % stops a space
\thanks{Manuscript received April 19, 2020; revised August 26, 2020.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) undergo a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  During Pulmonary Rehabilitation patients perform different exercises and walking activities and may require oxygen assistance.  The oxygen tank cannot be carried by the patient due to the eskeletomuscular atrophy that characterize this pathology and external assistance is required.   The assistance to transport the bulky oxygen tank can be provided by a robotic device that follows the patient while performing the physical activities. This work provides an initial study on the controlling mechanism of a differential tethered robot that implements a leader-follower configuration to carry the oxygen tank for these procedures.  Two alternative control strategies are proposed.  Results are simulated and tested on a real prototype in a Motion Capture System.
\end{abstract}

@@

\IEEEPARstart{C}{hronic} Obstructive Pulmonary Disease (COPD) is an umbrella term that describes several pulmonary affections.  They are characterized as a slowly progressive condition marked by airflow limitation, being cigarette smoking the main etiologic factor~\cite{MacNee2005}. This pathology presents an eskeletomuscular atrophy~\cite{Kocsis2016,Wu2012}. In order to carve these after effects a Pulmonary Rehabilitation procedure is a viable treatment for patients.  During this rehabilitation, patients undergo controlled walking activities and physical exercises under the supervision of a physical therapist.   Patients present a severe low oxygen saturation illness and they require effective oxygen supply, particularly when performing physical activity~\cite{Celli2014}.  Hence, patients require to carry with them an oxygen tank for the oxygenotherapy assistance.  However, their own condition prevent them with the ability to precisely carry the often bulky external tank.  This situation entails to find a pragmatic solution to avoid an additional physical therapist to carry the oxygen tank.  This scenario may be aggravated by the fact that this procedure is performed on a rehabilitation gym that could be potentially crowded with several patients, physiologists and physical therapists.

@@

An alternative solution is to use an assitive ground service robot~\cite{Neto2015} to carry the oxygen tank, while following the patient in a leader-follower configuration.  There are two reasons that support the initial viability of this idea.  First,  the rehabilitation gym is a constrained environment where this problem can be tackled by an Unmanned Ground Vehicle (UGV).  On the other hand, the range of movements performed by the patient during the Rehabilitation Procedure is highly predictable by the treatment.  At the same time,  the global robotic research community looks forward for the development of robotic affordable solutions to the social and health-related worldwide problems~\cite{Khamis2019}.

@@

Hence, this work provides an initial study on the controlling mechanism of a differential tethered robot that implements the leader-follower configuration on a Pulmonary Rehabilitation procedure.  To do so, this document unrolls as follows.  Section~\ref{materials} poses the problem and the solution design. Section~\ref{experimental} documents the experimental protocol to perform the solution assessment on a simulation and on a real world scenario.  Results and discussions are described in Sections ~\ref{results} and~\ref{discussion}. The clinical assessment performed jointly with medical personnel is tackled in Section~\ref{clinical}.  Finally, conclusions are exposed in the remaining Section~\ref{conclusion}.

@@

To be effective, any technological solution for the medical community requires active involvement of key stakeholders: physicians, care-givers, patients and their families~\cite{Gaggioli2006,Fasola2012,Cherubini2008,Wolpaw2012BraincomputerIP,Salvini2015}.  Hence, design methodologies that allow rapid prototyping can bring quickly feedback from real users about drawbacks or opportunities for improvements.

@@

    % Text Node
    \draw  [draw opacity=0][fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ]  (478.5,1350) -- (535.5,1350) -- (535.5,1374) -- (478.5,1374) -- cycle  ;
    \draw (507,1362) node    {$subject$};
    % Text Node
    \draw (302,1344) node    {$left\ reel\  \ $};
    % Text Node
    \draw (299,1425) node    {$right\ reel\  \ $};
    % Text Node
    \draw (125,1414) node    {$castor\ wheel$};
    % Text Node
    \draw (422,1348) node  [rotate=-12.55]  {$left\ thread$};
    % Text Node
    \draw (423,1422) node  [rotate=-344.79]  {$right\ thread$};
    % Text Node
    \draw (348,1275) node    {$left\ wheel$};
    % Text Node
    \draw (348,1496) node    {$right\ wheel$};
    \end{tikzpicture}
    \caption{Components of the robotic vehicle and the tether mechanism}
    \label{fig:components}
\end{figure}{}

@@

% El detalle de los encoders se puede eliminar, es info común.
Encoders in each reel measure the difference in length of each thread compared to its initial position. This difference in length is the input for the control algorithm.  Using the encoder, the difference in length for each thread can be measured with Equations~\ref{eq:encoder_len}.

\begin{equation}
\label{eq:encoder_len}
\begin{array}{ll}  
D_l = pulses_{l} \; \frac{2\pi r}{ppr}  \\
\\
D_r = pulses_{r} \; \frac{2\pi r}{ppr}
\end{array}
\end{equation}{}

\noindent where pulses obtained for each reel encoder are $pulses_{l}$ and $pulses_{r}$ for the left and right encoder. These equations provide the estimated values for the left $D_l$ and right $D_r$  thread distance. The variable $r$ is the radius of the reel and $ppr$ is the pulses per revolution (resolution) of the encoder.  The initial position of the threads is configurable.

@@

The SBC connects to a WiFi network and can receive remote commands to control the robot. It also broadcasts telemetry data to any listening devices on the network. The control algorithms run in this board, which continuously communicates with the Arduino board to receive sensor data and to issue commands to move the motors or retract the reels.   The algorithms are programmed in python 3.7, which allows the exact same code to run both the simulated and real world prototype.

@@

The two reels are designed from PVC extrusions and are shown on Figure~\ref{fig:alpibot2}.  They are attached to regular FA-12350 DC motors scavenged from old compact discs.  Each reel is axially locked to inexpensive Ky-040 rotary encoder which provides around 20 pulses per revolution.
%Hardware specifications are described on table \ref{tab:specifications}.

@@

As previously mentioned, an active spring mechanism is also put in place to keep the threads tense.  However, in order to extend the useful life of the reel motors, and to save battery, an algorithm to  activate and deactivate the motors is developed.

@@

Two simple algorithmic control strategies are proposed and evaluated.  The first one is called Follow-the-thread and the second strategy is Rotate and go.  %The Adafruit Shield controller provides a very stable output signal, provided battery are kept above reference.  Hence, wheels motor control is open-loop.

@@

This control strategy is similar to the one presented in \cite{Ortlieb2016}. It is based on the idea that the difference in length between both threads provides a quasi-linear function of the relative angle between the subject and the vehicle orientation and, additionally, the mean of both thread length allows to approximate the relative distance between the robot and the subject.  They are described by Equations~\ref{eq:lemniscata}, \ref{eq:lemniscata2} and~\ref{eq:lemniscata3}.

\begin{equation}
v_{tar} = c_v (\frac{D_l + D_r}{2} - d_0)
\label{eq:lemniscata}
\end{equation}

\begin{equation}
vleft_{tar} = v_{tar} + c_{\alpha} (D_l - D_r)
\label{eq:lemniscata2}
\end{equation}

\begin{equation}
vright_{tar} = v_{tar} - c_{\alpha} (D_l - D_r)
\label{eq:lemniscata3}
\end{equation}

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration.  As shown in Figure~\ref{fig:follow_params},  $D_l$ and $D_r$ are thread distances obtained from encoder information from Equation~\ref{eq:encoder_len}, $v_{tar}$ is the estimated forward velocity for the target and finally $vleft_{tar}$ are $vright_{tar}$ are the power values that are directly used to drive power to each wheel motor.

@@

\begin{equation}
\textit{if  }{\frac{D_l + D_r}{2} < d_0}\textit{ then } vleft_{tar} = vright_{tar} = 0 
\end{equation}

\noindent where $d_0$ is a constant offset that is used to customize the length of the thread where the robot does not move.

@@

    % Text Node
    \draw (524,1960) node  [font=\large,color={rgb, 255:red, 74; green, 144; blue, 226 }  ,opacity=1 ]  {$ \begin{array}{l}
    D_{r}\\
    \end{array}$};
    % Text Node
    \draw (510,1910) node  [font=\large,color={rgb, 255:red, 74; green, 144; blue, 226 }  ,opacity=1 ,rotate=-358.27]  {$ \begin{array}{l}
    D_{l}\\
    \end{array}$};
    % Text Node
    \draw (496,2042) node  [color={rgb, 255:red, 128; green, 128; blue, 128 }  ,opacity=1 ]  {$subject\ start$};
    % Text Node
    \draw  [draw opacity=0][fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ]  (554.5,1904) -- (611.5,1904) -- (611.5,1928) -- (554.5,1928) -- cycle  ;
    \draw (583,1916) node    {$subject$};
    % Text Node
    \draw (390.58,1925.93) node [anchor=west] [inner sep=0.75pt]  [font=\normalsize,color={rgb, 255:red, 0; green, 0; blue, 0 }  ,opacity=1 ]  {$vleft_{tar}$};
    % Text Node
    \draw (407.58,2100.93) node [anchor=west] [inner sep=0.75pt]  [font=\normalsize,color={rgb, 255:red, 0; green, 0; blue, 0 }  ,opacity=1 ]  {$vright_{tar}$};

@@

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_off$ that regulates the sensibility of the rotation movement.  The constant parameter $Dm_off$ is similar to $d_0$, and is used to customize the length of the thread where the robot does not move at all.

\begin{algorithm}[]
\caption{Rotate and go algorithm}
\begin{algorithmic}
\STATE $Dt \gets D_l - D_r$
\STATE $Dm \gets \frac{D_r+D_l}{2}$
\STATE $V_r \gets c_r * (abs(Dt) - Dt_off) + base_{vr}$ 
\STATE $V_f \gets c_v * (Dm - Dm_off)$

\IF{$abs(Dt) > Dt_{off}$}
\IF{$D_l > D_r$}
\STATE $vleft_{tar} \gets V_r$
\STATE $vright_{tar} \gets -V_r$
\ELSE
\STATE $vleft_{tar} \gets -V_r$
\STATE $vright_{tar} \gets V_r$
\ENDIF

\ELSE
\IF{$D_m > Dm_{off}$}
\STATE $vright_{tar} \gets V_f$
\STATE $vleft_{tar} \gets V_f$
\ELSE
\STATE $vright_{tar} \gets 0$
\STATE $vleft_{tar} \gets 0$
\ENDIF
\ENDIF
\STATE Return $vright_{tar}$ and $vleft_{tar}$.
\end{algorithmic}
\label{alg:rotateandgoalg}
\end{algorithm}
